PyUltraLight: A Pseudo-Spectral Solver for Ultralight Dark Matter Dynamics

### 2018-05-17 draft.tex
Minor formatting change
Rearranged sections as per RE's suggestion. Changes to the beginning of the Testing/Verification section.

\newcommand{\apj}{Astrophysical J.}
\newcommand{\prd}{Phys. Rev. D}
\newcommand{\mnras}{Mon. Notices Royal Astron. Soc}
\newcommand{\PyUltraLight}{\textsc{PyUltraLight}}

@@

\section{The Physics of ULDM: The Schr{\"o}dinger-Poisson System}\label{sec:physics}

@@

Summary of this section TBW

@@

@@

\section{Testing and Verification}\label{sec:test}

>>>>

\newcommand{\apj}{Astrophysical J.}
\newcommand{\prd}{Phys. Rev. D}
\newcommand{\mnras}{Mon. Notices Royal Astron. Soc}
\newcommand{\PyUltraLight}{\textsc{PyUltraLight }}

@@

\section{The Physics of ULDM}\label{sec:physics}

\subsection{The Schr{\"o}dinger-Poisson System}

@@

@@

In this section we discuss the methodology used to calculate the dynamics of the adimensional SP system (equations \ref{eq:s-adim} and \ref{eq:p-adim}) given user-specified initial conditions. We introduce the symmetrised split-step Fourier method, and describe schematically how the system is evolved at each timestep.

@@

\section{Verification of ULDM Dynamics}\label{sec:test}

In this section we test the validity of \PyUltraLight as a numerical SP solver by reproducing a number of results from previous studies of ULDM dynamics. We are able to reproduce phenomena arising due to the wavelike nature of ULDM, namely interference effects and effective repulsive forces. Additionally, we study the evolution of the velocity field within a solitonic core orbiting within a Newtonian central potential, showing that in the absence of complete tidal disruption, the stable orbital configuration is one of an irrotational Riemann-S ellipsoid. Finally, we demonstrate sub-percent level energy conservation for a selection of dynamical scenarios.
